Multisensor Architecture for an Intersection Management System

### 2015-06-09 ch2-mdf_ims.tex
Added table of IMS review, and added new bibtex entries to .bib file

In the next table is presented a compilation of several developments within IMS field. For each work a brief overview and a remark of how each component is related to it are given.

>>>>

In the table \ref{reviewtable} is presented a compilation of several developments within IMS field. For each work a brief comment is given, and a remark of how certain components (Data source, communication and application) are related to it. Target and implementation components could be infered from the comment.

\begin{center}
\footnotesize
\begin{longtable}{|c|p{0.3\linewidth}|p{0.15\linewidth}|p{0.1\linewidth}|c|}
%\begin{tabular}
\hline
\multicolumn{5}{|c|}{ \textbf{Developments on Intersection Management Systems} } \\

\hline
\textbf{Reference} & 
\pbox{0.3\linewidth}{\textbf{Comment}} & 
\pbox{0.15\linewidth}{\textbf{Application}} & 
\pbox{0.1\linewidth}{\textbf{Data Source}} & 
\textbf{Communication} \\

\hline
\endfirsthead
\hline
\textbf{Reference} & \textbf{Comment} & \textbf{Application} & \textbf{Data Source} & \textbf{Communication} \\
\hline
\endhead

\cite{Kamijo1999, Kamijo2000} & 
{They show an intersection monitoring system based on a fixed camera. This system is divided in three stages: Background modeling, object tracking and accident detection. They propose an innovative feature for accident detection using HMM.} & 
{Accident  detection} & 
Camera & 
N/A \\
\hline

\cite{Veeraraghavan2002} &
{Passive video-based system for monitoring an intersection. They implemented Stauffer's Method for background modeling, PCA for oriented bounding box computation, and Graph-based tracking and motion estimation. Also a simple methods for classification and calibration are described.} &
{Accident  detection} & 
Camera & 
N/A \\
\hline

\cite{Gehrig2003} & & & & \\
\hline

\cite{Veeraraghavan2003} &
They present 4 stages for IMS: background modeling, motion tracking, feature extraction, calibration. They propose a 2-level tracking: Blob tracking as low-level and position using Kalman filter as high-level. &
Accident detection / prediction &
Camera & 
N/A \\
\hline

\cite{Messelodi2004} & & & & \\
\hline
\cite{Dogan2004} & & & & \\
\hline

\cite{Chan2004} &
 &
 &
 &
 \\
\hline

\cite{Atev2005} &
 &
 &
 &
 \\
\hline

\cite{Chan2005} &
 &
 &
 &
 \\
\hline
\cite{Avila2005} &
 &
 &
 &
 \\
\hline

\cite{Veeraraghavan2005} &
 &
 &
 &
 \\
\hline

\cite{Zhao2006} &
 &
 &
 &
 \\
\hline

\cite{Eguchi2007} &
 &
 &
 &
 \\
\hline

\cite{Kuramoto2007} &
 &
 &
 &
 \\
\hline

\cite{Dresner2008} &
 &
 &
 &
 \\
\hline

\cite{Jarupan2008} &
 &
 &
 &
 \\
\hline

\cite{Zhao2008} &
 &
 &
 &
 \\
\hline

\cite{Rawashdeh2008} &
 &
 &
 &
 \\
\hline

\cite{Mundewadikar2008} &
 &
 &
 &
 \\
\hline

\cite{Zhao2009} &
 &
 &
 &
 \\
\hline

\cite{Abbas2009} &
 &
 &
 &
 \\
\hline

\cite{Babaei2010} &
 &
 &
 &
 \\
\hline

\cite{Meissner2010} &
 &
 &
 &
 \\
\hline

\cite{Quinlan2010} &
 &
 &
 &
 \\
\hline

\cite{Ball2010} &
 &
 &
 &
 \\
\hline

\cite{Babaei2011} &
 &
 &
 &
 \\
\hline

\cite{Basma2011} &
 &
 &
 &
 \\
\hline

\cite{Azimi2012} &
 &
 &
 &
 \\
\hline

\cite{CondeBento2012} &
 &
 &
 &
 \\
\hline

\cite{Zhao2012} &
 &
 &
 &
 \\
\hline

\cite{Jin2012} &
 &
 &
 &
 \\
\hline

\cite{Meissner2012} &
 &
 &
 &
 \\
\hline

\cite{Goldhammer2012} &
 &
 &
 &
 \\
\hline

\cite{Friesen2013} &
 &
 &
 &
 \\
\hline

\cite{} &
 &
 &
 &
 \\
\hline

\hline
%\end{tabular}
\caption{Developments related to Intersection Management Systems.}
\label{reviewtable}
\end{longtable}
\end{center}
